---
title: "stimuli_01"
author: "Misha Ash"
date: "5/1/2018"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(data.table)

set.seed(1111)

```

## framing

The present study aims to elicit a cognitive bias that derives from a mental metaphor that maps the dimension of emotional valence onto a vertical spatial dimension. For example, this metaphor might be deployed by representing the values along a non-spatial dimension ranging from negative emotions like sadness to positive emotions like happiness in terms of positions along a vertical spatial dimension ranging from low to high.

People vary in the valence and strength of their associations with concepts represented by words. For example, the name "Ludwig" might trigger strong positive feelings for someone who has fond memories of positive experiences with someone named Ludwig, which may affect how the happiness or sadness of Ludwig is interpreted. Alternatively, someone who has never known a Ludwig will likely be much more neutral in their affective response to this name, or their affective response may be colored by associations activated by resemblence with similar sounding words, such as "wig," or by their memories of the music of Ludwig van Beethoven or the arguments of Ludwig Wittgenstein. To mitigate and control for world knowledge effects on valence, the graphs will be presented as being about the happiness or sadness score of a fictional city. Three city names were generated on the [Fantasy Name Generators website](http://www.fantasynamegenerators.com/country_names.php#.Wup3DlMvzOR) (each two syllables):

*Oswa
*Escor
*Aflos


## design

The study is organized around a 2x2x2x3 design: 
*valence: positive (happiness), negative (sadness)
*direction: increasing, decreasing
*grid lines: 0 (labels at 0 and 100) and 1 (mid-line added at 50)
*city name: Oswa, Escor, Aflos (control variable)

Within-subjects designs can increase power for a given sample size. However, the comparability (and power) gained would require either using the same values for stimuli across conditions, which is prone to order effects and would require extensive counter-balancing resulting in the need for a larger sample, or different values across conditions that vary between participants to converge on comparable means, which would require a larger stimulus set and a larger sample. Given the exploratory nature of the current experiment, a one-shot, between-subjects design is used. The study will consist of one HIT with one of 8 possible conditions, randomly assigned and balanced. Each visualization will display the same three data points in ascending or descending order.

The estimation will be made with recall. 


A set of 8 stimuli graphs is generated by crossing these factors
```{r}
direction <- c("increasing", "decreasing")
valence <- c("happiness", "sadness")
gridlines <- c(0, 1)
city <- c("Oswa", "Escor", "Aflos")

conditions <- CJ(direction, valence, gridlines, city) %>%
  setnames("V1", "direction") %>%
  setnames("V2", "valence") %>%
  setnames("V3", "gridline") %>%
  setnames("V4", "city")
```

 
## data for visualization

The data value triplet used across the graphs is randomly sampled from its respective third of the 0 - 100 range ±5 (to keep the value from being directly on a grid line and force estimation). The method used by the base R sampling function is analogous to Cleveland and McGill's use of a "uniform random number generator" (1984, p. 539).  
  
```{r}
min_value <- base::sample(5:28, 1, replace = FALSE)
mid_value <- base::sample(39:61, 1, replace = FALSE)
max_value <- base::sample(72:95, 1, replace = FALSE)

data_source <- c(min_value, mid_value, max_value) %>%
  as_data_frame() %>%
  mutate(increasing = c(2015, 2016, 2017)) %>%
  mutate(decreasing = c(2017, 2016, 2015))
```

## stimulus graphs

### condition 1: dec_hap_Alfos_nogrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Alfos') +
        xlab('') +
        ylab('Happiness Score')

ggsave("1 dec_hap_Alfos_nogrid.png", width = 7, height = 5)
```
### condition 2: dec_hap_Escor_nogrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Escor') +
        xlab('') +
        ylab('Happiness Score')

ggsave("2 dec_hap_Escor_nogrid.png", width = 7, height = 5)
```
### condition 3: dec_hap_Oswa_nogrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Oswa') +
        xlab('') +
        ylab('Happiness Score')

ggsave("3 dec_hap_Oswa_nogrid.png", width = 7, height = 5)
```






### condition 4: dec_hap_Alfos_wgrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Alfos') +
        xlab('') +
        ylab('Happiness Score')

ggsave("4 dec_hap_Alfos_wgrid.png", width = 7, height = 5)
```
### condition 5: dec_hap_Escor_wgrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Escor') +
        xlab('') +
        ylab('Happiness Score')

ggsave("5 dec_hap_Escor_wgrid.png", width = 7, height = 5)
```
### condition 6: dec_hap_Oswa_wgrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Oswa') +
        xlab('') +
        ylab('Happiness Score')

ggsave("6 dec_hap_Oswa_wgrid.png", width = 7, height = 5)
```













### condition 7: dec_sad_Alfos_nogrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Alfos') +
        xlab('') +
        ylab('Sadness Score')

ggsave("7 dec_sad_Alfos_nogrid.png", width = 7, height = 5)
```
### condition 8: dec_sad_Escor_nogrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Escor') +
        xlab('') +
        ylab('Sadness Score')

ggsave("8 dec_sad_Escor_nogrid.png", width = 7, height = 5)
```
### condition 9: dec_sad_Oswa_nogrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Oswa') +
        xlab('') +
        ylab('Sadness Score')

ggsave("9 dec_sad_Oswa_nogrid.png", width = 7, height = 5)
```

### condition 10: dec_sad_Alfos_wgrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Alfos') +
        xlab('') +
        ylab('Sadness Score')

ggsave("10 dec_sad_Alfos_wgrid.png", width = 7, height = 5)
```
### condition 11: dec_sad_Escor_wgrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Escor') +
        xlab('') +
        ylab('Sadness Score')

ggsave("11 dec_sad_Escor_wgrid.png", width = 7, height = 5)
```
### condition 12: dec_sad_Oswa_wgrid
```{r}
data_source %>%
  
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Oswa') +
        xlab('') +
        ylab('Sadness Score')

ggsave("12 dec_sad_Oswa_wgrid.png", width = 7, height = 5)
```



















### condition 13: inc_hap_Alfos_nogrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Alfos') +
        xlab('') +
        ylab('Happiness Score')

ggsave("13 inc_hap_Alfos_nogrid.png", width = 7, height = 5)
```

### condition 14: inc_hap_Escor_nogrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Escor') +
        xlab('') +
        ylab('Happiness Score')

ggsave("14 inc_hap_Escor_nogrid.png", width = 7, height = 5)
```

### condition 15: inc_hap_Oswa_nogrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Oswa') +
        xlab('') +
        ylab('Happiness Score')

ggsave("15 inc_hap_Oswa_nogrid.png", width = 7, height = 5)
```








### condition 16: inc_hap_Alfos_wgrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Alfos') +
        xlab('') +
        ylab('Happiness Score')

ggsave("16 inc_hap_Alfos_wgrid.png", width = 7, height = 5)
```

### condition 17: inc_hap_Escor_wgrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Escor') +
        xlab('') +
        ylab('Happiness Score')

ggsave("17 inc_hap_Escor_wgrid.png", width = 7, height = 5)
```

### condition 18: inc_hap_Oswa_wgrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in Oswa') +
        xlab('') +
        ylab('Happiness Score')

ggsave("18 inc_hap_Oswa_wgrid.png", width = 7, height = 5)
```












### condition 19: inc_sad_Alfos_nogrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Alfos') +
        xlab('') +
        ylab('Sadness Score')

ggsave("19 inc_sad_Alfos_nogrid.png", width = 7, height = 5)
```

### condition 20: inc_sad_Escor_nogrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Escor') +
        xlab('') +
        ylab('Sadness Score')

ggsave("20 inc_sad_Escor_nogrid.png", width = 7, height = 5)
```

### condition 21: inc_sad_Oswa_nogrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Oswa') +
        xlab('') +
        ylab('Sadness Score')

ggsave("21 inc_sad_Oswa_nogrid.png", width = 7, height = 5)
```


### condition 22: inc_sad_Alfos_wgrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Alfos') +
        xlab('') +
        ylab('Sadness Score')

ggsave("22 inc_sad_Alfos_wgrid.png", width = 7, height = 5)
```

### condition 23: inc_sad_Escor_wgrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Escor') +
        xlab('') +
        ylab('Sadness Score')

ggsave("23 inc_sad_Escor_wgrid.png", width = 7, height = 5)
```

### condition 24: inc_sad_Oswa_wgrid
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Sadness in Oswa') +
        xlab('') +
        ylab('Sadness Score')

ggsave("24 inc_sad_Oswa_wgrid.png", width = 7, height = 5)
```














## qualification test

```{r data}
data_qualification <- c(25, 50, 75) %>%
  as_data_frame() %>%
  mutate(increasing = c(2015, 2016, 2017)) %>%
  mutate(decreasing = c(2017, 2016, 2015))
```
qualification test stim (increasing)
```{r}
data_qualification %>%
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 25, 50, 75, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
  # change color scheme of fill colors
    scale_color_manual("color", values = wes_palette(name = "Zissou")) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
    ggtitle('') +
    xlab('') +
    ylab('')

ggsave("qual_test_increasing.png")
```

qualification test stim (decreasing)
```{r}
data_qualification %>%
  ggplot(aes(decreasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 25, 50, 75, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
  # change color scheme of fill colors
    scale_color_manual("color", values = wes_palette(name = "Zissou")) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
    ggtitle('') +
    xlab('') +
    ylab('')

ggsave("qual_test_decreasing.png")
```




## vestiges
```{r}
data_source %>%
  
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
        ggtitle('Happiness in A') +
        xlab('') +
        ylab('Happiness')

ggsave("....png")
```


increasing happiness visualization (compatible)
```{r}
#plot <- 
  
  data_source %>%
  ggplot(aes(increasing, value)) +
  geom_line(size = 0.4) +
  geom_point() +

  scale_y_continuous(limits = c(0, 100), breaks = c(0, 100), expand = c(0, 0)) +
  scale_x_continuous(limits = c(2014.9, 2017.1), breaks = c(2015, 2016, 2017)) +
  
  # change color scheme of fill colors
    scale_color_manual("color", values = wes_palette(name = "Zissou")) +
  
    theme_light() +
    theme(panel.grid.major.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.x = element_blank(), # remove vertical grid lines
        panel.grid.minor.y = element_blank(), # remove minor horizontal grid lines
        #panel.grid.major.y = element_line(size = 0.5),
        panel.border = element_blank(),
        axis.line = element_line(size = 0.15),
        
        plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0)),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)), 
        axis.ticks.x = element_line()) +
  
    ggtitle('Happiness in A') +
    xlab('') +
    ylab('Happiness Score')
```



